---
title: "Lab-11 Replication"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This notebook replicates Lab-11.

## Dependencies
This notebook requires only a few packages:

```{r load-packages}
# tidyverse packages
library(ggplot2)      # data plotting

# other packages
library(here)         # file path management
library(testDriveR)   # data
```

## Load Data
This notebook requires the `auto17` data from `testDriveR`:

```{r load-data}
autoData <- auto17
```

## Part 1: Regression Model 1
## Question 1

The following code creates a scatter plot comparing fuel cost to displacement (in liters). The plot uses the `jitter` position to make points more visible, and colors the points using the variable `gears` transformed into a factor variable. It also has a linear model overlaid.

```{r p1-q1-plot}
ggplot(data = autoData, mapping = aes(x = displ, y = fuelCost)) +
  geom_point(mapping = aes(color = as.factor(gears)), position = "jitter") +
  geom_smooth(method = "lm")
```

There is a clear linear relationship between fuel cost and engine size. The larger the engine, the higher the fuel cost. The relationship with gears is less clear. There does seem to be a general pattern where higher geared cars have higher fuel cost, but there are also a high number of cars with 8 gears that have small engines and relatively low fuel cost.

```{r p1-q1-save}
ggsave(filename = here("results", "scatter_displ_fuel.png"), dpi = 300)
```

## Question 2

The hypotheses we are testing are:

* H0 - engine size does not have an impact on a car's annual fuel cost
* H1 - engine size does have an impact on a car's annual fuel cost - the higher the engine size, the higher the expected fuel costs.

## Question 3

The equation for the regression model in question 4 is:

$ {y}_{fuelCost} = \alpha + {\beta}_{1}{x}_{displ} + \epsilon $

## Question 4

The following saves the results of the linear model specified in question 3 into the object `model`, and then reports a summary of the linear model's results.

```{r p1-q4}
model <- lm(fuelCost ~ displ, data = autoData)
summary(model)
```

A unit increase in displacement is associated with an increase in fuel cost. For every liter increase in displacement, the average cost of fuel per year rises \$283.83 ($p<.001$). Overall, engine size accounts for 67.71% of the variation in fuel cost.

## Part 2: Regression Model 2
## Question 5

The following code creates a scatter plot comparing fuel cost to highway fuel efficiency (in miles per gallon). The plot uses the `jitter` position to make points more visible, and colors the points using the variable `cyl` transformed into a factor variable. It also has a linear model overlaid.

```{r p2-q5-plot}
ggplot(data = autoData, mapping = aes(x = hwyFE, y = fuelCost)) +
  geom_point(mapping = aes(color = as.factor(cyl)), position = "jitter") +
  geom_smooth(method = "lm")
```

Once again, there is a clear relationship between fuel cost and highway fuel efficiency. The more efficient cars also have lower fuel costs. The relationship, however, does not be linear. Unlike the previous plot, the patterning with cylinders is clearer than gears - cars with a larger number of cylinders have both higher fuel costs and lower highway fuel efficiency. 

```{r p2-q5-save}
ggsave(filename = here("results", "scatter_hwy_fuel.png"), dpi = 300)
```

## Question 6

The hypotheses we are testing are:

* H0 - highway fuel efficiency does not have an impact on a car's annual fuel cost
* H1 - highway fuel efficiency does have an impact on a car's annual fuel cost - the higher the fuel efficiency, the lower the expected fuel costs.

## Question 7

The equation for the regression model in question 8 is:

$ {y}_{fuelCost} = \alpha + {\beta}_{1}{x}_{hwyFE} + \epsilon $

## Question 8

The following saves the results of the linear model specified in question 7 into the object `model`, and then reports a summary of the linear model's results.

```{r p2-q8}
model <- lm(fuelCost ~ hwyFE, data = autoData)
summary(model)
```

A unit increase in highway fuel efficiency is associated with an decrease in fuel cost. For every mile per gallon increase in efficiency, the average cost of fuel per year decreases \$69.65 ($p<.001$). Overall, highway fuel efficiency accounts for 79.22% of the variation in fuel cost.
