\documentclass{tufte-handout}

\usepackage{xcolor}

% set image attributes:
\usepackage{graphicx}
\graphicspath{ {images/} }

% set hyperlink attributes
\hypersetup{colorlinks}

% create environment for bottom paragraph:
\newenvironment{bottompar}{\par\vspace*{\fill}}{\clearpage}

\usepackage{enumerate}

% set table attributes
\usepackage{tabu}
\usepackage{booktabs}

% ============================================================

% define the title
\title{SOC 4015/5050: Lab-11 - Bivarite Regression}
\author{Christopher Prener, Ph.D.}
\date{Fall 2018}

% ============================================================

\begin{document}

% ============================================================

\maketitle % generates the title

% ============================================================

\vspace{5mm}
\section{Directions}
Please complete all steps below. All work should be uploaded to your GitHub assignment repository by 4:15pm on Monday, November 19\textsuperscript{th}, 2018. All data can be obtained from the \texttt{testDriveR} package's \texttt{auto17} data set.

\vspace{5mm}
\section{Analysis Development}
Using RStudio and your operating system's file manager, create an R Project in the \textit{existing} directory in your assignments repository named \texttt{Lab-11}. Add a \texttt{README.md} file, notebook, and all necessary folders before beginning.\sidenote{This initial section follows the project workflow that is available in the \texttt{lecture-03} repo!}

\vspace{3mm}
\section{Regression Model 1}
\begin{enumerate}
\item Construct a dissemination ready scatter plot of the relationship between fuel cost (\texttt{fuelCost}) and engine size (\texttt{displ}). Include a linear regression line on the plot and color the points based on the number of gears (\texttt{gears}). 
\item Construct a hypothesis and null hypothesis for the relationship between fuel cost (\texttt{fuelCost}) and engine size (\texttt{displ}).
\item Construct a regression equation modeling how \texttt{displ} affects \texttt{fuelCost} using \LaTeX{}\ syntax.
\item Execute a bivariate regression model that shows how \texttt{displ} affects \texttt{fuelCost}. Fully interpret the results of this model.
\end{enumerate}

\vspace{3mm}
\section{Regression Model 2}
\begin{enumerate}
\setcounter{enumi}{4}
\item Construct a hypothesis and null hypothesis for the relationship between fuel cost (\texttt{fuelCost}) and highway fuel efficiency (\texttt{hwyFE}).
\item Construct a dissemination ready scatter plot of the relationship between fuel cost (\texttt{fuelCost}) and highway fuel efficiency (\texttt{hwyFE}). Include a linear regression line on the plot and color the points based on the number of cylinders (\texttt{cyl}). 
\item Construct a regression equation modeling how \texttt{hwyFE} affects \texttt{fuelCost} using \LaTeX{}\ syntax.
\item Execute a bivariate regression model that shows how \texttt{hwyFE} affects \texttt{fuelCost}. Fully interpret the results of this model.
\end{enumerate}


% ============================================================
\end{document}